Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-01 alloscore_manuscript/supplement.rnw
write down TQ equation to prepare for alloscore algo discussion

$TQ_F$ satisfies the conditions mentioned in section \ref{sec:quantile-functions} for being a quantile function, and so there
is a random variable $TY_F$ with cdf $F_{T} := F_{TQ_F}$.  From this perspective, the problem of finding $\tau$ becomes the calculation 
of $F_{T}(K) = \mathbb{P}(TY_F \leq K)$, making clear the existence of a solution $\tau^{\star}$ to \eqref{eqn:tau-inclusion}.

@@

>>>>

$TQ_F$ satisfies the conditions mentioned in section \ref{sec:quantile-functions} for being a quantile function, and so there
is a random variable $TY_F$ with cdf $F_{T} := F_{TQ_F}$.  From this perspective, the problem of finding $\tau$ becomes the calculation 
of $F_{T}(K) = \mathbb{P}(TY_F \leq K)$, making clear the existence of a solution $\tau^{\star}$ to \eqref{eqn:tau-inclusion}. This also
yields the interesting formal expression of the Bayes act
\begin{align}
x^{F,K} = (F_1,\ldots,F_N)^{-1}(\mathbf{1}_N F_{T}(K)),
\end{align}
where $\mathbf{1}_N: \mathbb{R} \to \mathbb{R}^N$ is the linear map that takes $a$ to the $N$-vector $(a,\ldots,a)^T$ and 
$(F_1,\ldots,F_N)^{-1}$ is a map from $\mathbb{R}^N$ to $\mathbb{R}^N$. We can also arrange this as
\begin{align}
TQ_F\left(\frac{1}{N} \mathbf{1}^T (F_1,\ldots,F_N)(x^{F,K})\right) = K,
\end{align}
which leads conceptually to the iterative numerical method of solving for $x^{F,K}$ discussed next in section \ref{sec:numeric}.

@@

\section{Numerical computation of allocation scores}
\label{sec:numeric}
